**Challenge Name**  
Friendship Queries

**Description**  
Answer Check and Connect queries based on friendship

**Problem Statement**  
The Treasurer of [CS-GPDC](https://www.linkedin.com/company/cs-gpdc), [Nikita](https://www.linkedin.com/in/nikita-menon-267523112/), is a social person, and she enjoys hanging out with friends. To teach some kids the importance of having a friend circle to some kids, she wants to play a game with them. There are $N$ kids in a garden, and you are responsible for creating friend circles among them. Nikita will ask you $Q$ queries of types $Connect$ and $Check$ based on the friendship of two kids $x$ and $y$. For a query of type $Connect$, connect $x$ and $y$, including their friend circles, and answer with the size of the newly formed friend circle. If $x$ and $y$ are already friends, answer with the size of their existing friend circle. For a query of type $Check$, check whether $x$ and $y$ are friends. If they are friends, answer with the size of their friend circle, otherwise answer with -1.  

**Sample Example**  

```text
4 4
Check 0 3
Connect 0 1
Connect 3 1
Check 0 3
```

Initially, we have 4 kids and 4 friend circles (with just one kid in each).  
The friend circles are- <0> <1> <2> <3>  

`Check 0 3`  
Since 0 and 3 are not friends, we answer with -1.  

`Connect 0 1`  
We connect 0 and 1.  
The friend circles are- <0, 1> <2> <3>  

`Connect 3 1`  
We connect 3 and 1.  
The friend circles are- <0, 1, 3> <2>  

`Check 0 3`  
Since 0 and 3 are now friends, we answer with the size of their friend circle, 3.  



**Input Format**  
The first line contains two space-separated integers $N$, the number of kids, and $Q$, the number of queries.  
The next $Q$ lines are of the form <$type$ $x$ $y$> where the string $type$ is either $Connect$ or $Check$, and $x$ and $y$ are the two kids. ($x$, $y$ are 0-indexed.)

**Constraints**  
$1 \leq N, Q \leq 10^5$  
$0 \leq x, y \leq (N-1)$  

**Output Format**  
Print the answer of each query on a new line.
